\section{\texorpdfstring{The $\Wln$  Signal Extraction}{The W-> l nu  Signal Extraction}}
\label{sec:WsignalExtraction}

The signal and background yields are obtained by fitting
the $\MET$ distributions for $\Wen$ and $\Wmn$ to different
functional models.
An accurate $\MET$ measurement is essential for distinguishing
a $\PW$ signal from QCD multijet backgrounds.
We profit from the application of the PF
algorithm, which provides superior $\MET$
reconstruction performance~\cite{PFMET1} with respect to alternative
algorithms at the energy scale of the $\PW$ boson.
% The energy of photons is directly obtained from the ECAL measurement,
% corrected for zero-suppression effects.
% The energy of electrons is determined from a combination of the track
% momentum at
% the main interaction vertex, the corresponding ECAL cluster energy,
% and the energy sum of
% all bremsstrahlung photons attached to the track. The energy of muons
% is obtained from the
% corresponding track momentum. The energy of charged hadrons is
% determined from a combination
% of the track momentum and the corresponding ECAL and HCAL energy,
% corrected for
% zero-suppression effects, and calibrated for the non-linear response
% of the calorimeters. Finally
% the energy of neutral hadrons is obtained from the corresponding
% calibrated ECAL and HCAL
% energy.


The $\MET$ is the magnitude of the transverse component of the missing momentum
vector, computed as the negative of the vector sum of all
reconstructed transverse momenta of particles identified with
the PF algorithm. The algorithm combines the information from
the inner tracker, the muon chambers, and the calorimeters
to classify reconstructed objects according to particle type
(electron, muon, photon, or charged or neutral hadron),
thereby allowing precise energy corrections.
The use of the tracker information reduces the sensitivity of $\MET$ to miscalibration of the calorimetry.
%also providing a significant degree of redundancy that
%reduces the sensitivity of the $\MET$ measurements
%to miscalibrations of the calorimetry.
%\par
%The impact of anomalous noise signal in the calorimeters is reduced to
%a negligible level~\cite{metPAS}.

\par
The QCD multijet background is one of the most significant backgrounds in W analyses.
At high $\MET$, EWK backgrounds, in particular $\Wtn$ and DY,
also become relevant, leading to contamination levels on the
order of $10\%$.

The $\MET$ model is fitted to the observed distribution as the sum of three contributions:
the W signal, the QCD and EWK backgrounds.
The EWK contributions are normalized to the W signal yield in the fit
through the ratios of the theoretical cross sections.

Simultaneous fits are performed to the two $\MET$ spectra of W$^+$ and W$^-$ candidates,
fitting either the total W cross section and
the ratio of positive and negative W cross sections, or
the individual positive and negative W cross sections.
In both cases the overall normalization of QCD multijet events is determined from the fit.
The diboson and $\ttbar$ contributions,
taken from simulations, are negligible (Section~\ref{sec:EWKbkgds}).


\par
In the following sections the modeling
of the $\MET$ shape for the signal and the EWK backgrounds is presented,
and the methods used to determine
the $\MET$ shape for the QCD multijet background from data are
 described.
Finally, the extraction of the signal yields is discussed.



%\input{MET}

\input{W-EWK-template}

\input{W-EWK-Backgrounds.tex}

\input{W-QCD-template}

\input{Wmn.tex}


\section{\texorpdfstring{The $\Zll$ Signal Extraction}{The Z-> ll Signal Extraction}}
\label{sec:ZsignalExtraction}

The $\Zll$ yield can be obtained by counting the
number of selected candidates after subtracting the residual background.
The $\Zll$ yield and lepton efficiencies are also determined using a simultaneous fit
to the invariant mass spectra of multiple dilepton categories.
The simultaneous fit deals correctly with correlations
in determining the lepton efficiencies and the $\Zo$ yield
from the same sample.
The Z yield extracted in this way does not need to be corrected for efficiency effects
in order to determine the cross section, and
the statistical uncertainty on the $\Zo$ yield absorbs the uncertainties
on the determination of lepton efficiencies that would be propagated as systematic
uncertainties in the counting analysis.
Both methods were performed for the $\Zee$ analysis, while only
the simultaneous fit was used for the $\Zmm$ analysis
after taking into account the results from the previous studies~\cite{WZCMS:2010}.
%at lower luminosity which disfavour the use of the counting analysis.

\subsection{EWK and QCD Backgrounds}
\label{sec:bkgZll}

For the $\Zee$ analysis the background contributions from EWK processes $\Ztt$, $\ttbar$,
and diboson production are estimated from the yields of events selected in NLO MC samples
normalized to the NNLO cross sections and scaled to the considered integrated luminosity.
They amount to \ZEEEWKBKG events, where the uncertainty combines the NNLO
and luminosity uncertainties. Data are used to estimate the background
originating from W+jets, $\gamma$+jets, and QCD multijet events where the
selected electrons come from misidentified jets or photons
(referred to as 'QCD background').
This background contribution is estimated using the distribution
of the relative track isolation, $\ITRK/\Et$,
and amounts to $4.9 \pm 8.4\, \textrm{(stat.)} \pm 8.4\, \textrm{(syst.)}$ events.
As a cross-check, the ``same-sign/opposite-sign'' method was used,
which is based on the signs of the charges of the two electron candidates, the measured
charge misidentification for electrons that pass the nominal selection criteria, and the
hypothesis that the QCD background is charge-symmetric.
The QCD background estimate with this method is $59 \pm 17
\textrm{(stat.)} \pm 160\, \textrm{(syst.)}$ events.
The two methods are consistent with the presence of negligible QCD background in our sample.

Backgrounds in the $\Zmm$ analysis containing two isolated global muons
have been estimated with simulations to be very small.
This category of dimuon events is defined as the ``golden'' category.
The simulation prediction of the smallness of the $\ttbar$ and QCD backgrounds was validated with data.
First, the selected dimuon sample was enriched with $\ttbar$ events by applying
a requirement on $\MET$, because of the presence of neutrinos in $\ttbar$ events,
and an agreement between data and the simulation prediction was found
with the dimuon invariant mass requirement inverted,
where the residual Z signal is negligible.
The QCD component has been checked using the same-sign dimuon events and dimuon events with
both muons failing the isolation requirement, and was found to be in agreement with the simulation predictions.
The conclusion from the maximum amount of measured data-simulation discrepancy
was that the uncertainty in the residual background subtraction
has a negligible effect on the $\Zmm$ measured yield.
The backgrounds to the $\Zmm$ categories having one global and one looser muon
are significantly larger than in the golden category.
Simulation estimates in this case are not used for such backgrounds and
fits to the dimuon invariant mass
distributions are performed including parameterized background components, as
described in Section~\ref{sec:Zmumu}.

Backgrounds estimates in the $\Zee$ and $\Zmm$ analyses are summarized in Table~\ref{tab:ZllBG}.
%--------------------------------------------------
\begin{table} %
\begin{center}
\caption[.]{\label{tab:ZllBG}
Estimated background-to-signal ratios in the $\Zee$ and $\Zmm$ (only for candidates
in the golden category) channels.
The QCD background for the $\Zee$ channel has been estimated with data,
while all other estimates are based on MC simulations, and their corresponding uncertainties
are statistical only.}
\begin{tabular}{|l|c|c|}
\hline
Processes & $\Zee$ sel. & $\Zmm$ sel. \\
\hline\hline
Diboson production   & $(0.157\pm 0.001)\%$ & $(0.158\pm 0.001)\%$ \\
$\ttbar$             & $(0.117\pm 0.008)\%$ & $(0.141\pm 0.014)\%$ \\
$\Ztt$               & $(0.080\pm 0.006)\%$ & $(0.124\pm 0.005)\%$ \\
W+jets               & $(0.010\pm 0.002)\%$ & $(0.008\pm 0.002)\%$ \\
\hline
Total EWK plus $\ttbar$  & $(0.365\pm 0.010)\%$ & $(0.430\pm 0.015)\%$ \\
\hline
QCD            & $(0.06\pm 0.14)\%$ &  $(0.013\pm 0.001)\%$ \\
\hline
Total background                & $(0.42\pm 0.14)\%$ & $(0.444\pm 0.015)\%$ \\
\hline
\end{tabular}
\end{center}
\end{table}



%--------------------------------------------------


\input{Zee}

\input{Zmm}
